### 2011-07-11 doc/theses/svirec/kap3.tex
first part of the proposed algorithm

\section[Repairs and Consistent Answers for XML Data]{Repairs and Consistent Answers for XML Data with Functional Dependencies}

@@

\begin{define}[R-XML Tree]
A R-XML $tree$ is a triplet $RXT = \langle T, \delta, \varrho \rangle$, where $\langle T, \delta \rangle$ is an XML tree and $\varrho$ is a reliability function from $N_T$ to \texttt{\{true, false\}}, such that, for each pair of nodes $n_1 , n_2 \in N_T$ with $n_2$ descendant of $n_1$, it holds that $\varrho(n_1) = false \Rightarrow \varrho(n_2) = false$.\qed
\end{define}

>>>>

\section[Repairs and Consistent Answers for XML Data]{Repairs and Consistent Answers for XML Data with Functional Dependencies}\label{RepConstAnswers}

@@

\begin{define}[R-XML Tree]\label{rxmlTree}
A R-XML $tree$ is a triplet $RXT = \langle T, \delta, \varrho \rangle$, where $\langle T, \delta \rangle$ is an XML tree and $\varrho$ is a reliability function from $N_T$ to \texttt{\{true, false\}}, such that, for each pair of nodes $n_1 , n_2 \in N_T$ with $n_2$ descendant of $n_1$, it holds that $\varrho(n_1) = false \Rightarrow \varrho(n_2) = false$.\qed
\end{define}
